Exploring United States Housing Affordability

### 2016-08-10 paper/Paper.Rmd
paper grammer

library(ggplot2)
library(dplyr)
library(readr)
library(stringr)
library(xml2)
library(rvest)
library(tidyr)
library(purrr)
library(scales)
library(maps)
library(ggthemes)
```
#Abstract

##Introduction

@@

  The goal is to determine whether housing affordability has increased or decreased over the last few decades. Our initial hypothesis assumes that housing affordability within the United States has decreased due to key, significant events that have occurred within the last few years. The United State's growing income inequality can be attributed to the current state of housing affordability, and is a clear indicator of the shifting income brackets between who is poor and who is rich. Another major event that could have potentially affected the current state of housing affordability, is the 2007 Housing Market crash that affected the entire country, and even the world. Amongst all of the foreclosures, loan defaults, and stock market crash, we will closely examine the years between 2007 and 2011 to capture a better sense of the status of the housing market's affordability.

###Cleaning data

@@

###Analyzing the Data

  The main metric that is referred to in this paper is burden. Burden is defined by the proportion of household income that is spent towards the cost of housing. This metric is then further dissected by analyzing against various variables and collating data on contributing factors, such as income. The first data explored is income data across the four designated regions in the United States (Northeast, Midwest, South, West). The adjusted incomes (per persons and per bedroom) are also considered, as certain regions may have different averages for household and property sizes, which could skew the unadjusted income data. The behavior of household income, bracketed in ranges in accordance to census data, over time is displayed to provide a better understanding of the changes in burden over time. The household incomes are then compared versus burden over time. here it is found that the higher income levels generally have lower housing burdens, and those burdens actually decrased over time, while burdens in the lower income brackets were generally higher and increased over time. Also, the housing burdens in the Northeast and West are generally higher than the Midwest and South. Finally, to elucidate the gap in burden levels across high and low incomes, the housheold burden amongst owners and renters, and those with and without governement assistance is considered. Here it is found that owning households tend to have lower burden levels, as do those households with no assistance.

###Graphical findings

@@

##Conclusion:

>>>>

library(ggplot2)
library(dplyr)
library(readr)
library(stringr)
library(xml2)
library(rvest)
library(tidyr)
library(purrr)
library(scales)
library(maps)
library(ggthemes)
```

<br>
<br>
<br>

#Abstract

@@

  The goal is to determine whether housing affordability has increased or decreased over the last few decades. Our initial hypothesis assumes that housing affordability within the United States has decreased due to key, significant events that have occurred within the last few years. The United State's growing income inequality can be attributed to the current state of housing affordability, and is a clear indicator of the shifting income brackets between who is poor and who is rich. Another major event that has potential consequences on the current state of housing affordability, is the 2007 Housing Market crash. Amongst all of the foreclosures, loan defaults, and stock market crash, we will closely examine the years between 2007 and 2011 to capture a better sense of the status of the housing market's affordability.

The main metric that is referred to in this paper is burden. Burden is defined by the proportion of household income that is spent towards the cost of housing. This metric is then further dissected by analyzing against various variables and collating data on contributing factors, such as income. The first data explored is income data across the four designated regions in the United States (Northeast, Midwest, South, West). The adjusted incomes (per persons and per bedroom) are also considered, as certain regions may have different averages for household and property sizes, which could skew the unadjusted income data. The behavior of household income, bracketed in ranges in accordance to census data over time, is displayed to provide a better understanding of the changes in burden over time. The household incomes are then compared versus burden over time. It is found that the higher income levels generally have lower housing burdens, and those burdens actually decrased over time, while burdens in the lower income brackets were generally higher and increased over time. Also, the housing burdens in the Northeast and West are generally higher than the Midwest and South. Finally, to elucidate the gap in burden levels across high and low incomes, the housheold burden amongst owners and renters, and those with and without governement assistance is considered. Here it is found that owning households tend to have lower burden levels, as do those households with no assistance.

##Cleaning the Data

@@

##Graphical findings

@@

#Conclusion:
